### 2020-08-11 response/response-demography-3.tex

\begin{document}

\begin{center} \textbf{\large Birth Spacing in the Presence of Son
Preference and 
Sex-Selective Abortions: India's Experience over Four Decades}
\end{center}

\begin{center} Response to Editor and Reviewer Comments \end{center}

\noindent Please find attached the revised version of my paper,
``Birth Spacing in the Presence of Son Preference and Sex-Selective
Abortions: India's Experience over Four Decades.''
Thank you for the comments and suggestions. 
Below I outline my response to each issue raised.

As part of rewriting the paper in response to the comments, I have changed a number of 
additional parts to ensure that the paper is easier to follow and understand.
The following are some of the more substantial changes not covered below in my responses:
\begin{enumerate}
    \item The Abstract has been substantially rewritten to directly address the three
    main questions I address in the paper
	\item Rewritten ``Estimation Strategy'' section:
	\begin{enumerate}
		\item Clarify proportionality assumption
		\item Better explain set-up of model and transformation of data needed
		\item Remove discussion of explanatory variables so they are
		only covered once (in the ``Data'' section)
		\item Better explanation of how I calculate measures used for the spacing
		analysis and all explanations gathered in this section
		\item Remove the formular for percent boys since it added little to the
		explanation. 
		I have added a more formal version of the model to the online Appendix in the
		``Empirical Model Details'' section.
	\end{enumerate}
	\item Changes in ``Data'' section:
	\begin{enumerate}
		\item Lead with what birth spells I analyze right after introducing
		data
		\item Move discussion of restriction to only Hindus to be the first since that is 
		the most important. 
		See also response to Reviewer 2 below.
	\end{enumerate}
	\item Ensure consistent presentation of results:
	\begin{enumerate}
		\item Update table notes to more clearly describe calculation methods
	\end{enumerate}
\end{enumerate}

@@

\begin{enumerate}

\item We note that you kept to the table/figure limit; however, some of
the figures are several pages long and relatively small. These will have
to be evaluated at the copy edit stage as there is no obvious quick fix
- the figures reflect the analyses carried out (and some additional ones
are in an online appendix). Please make sure to submit as
high-resolution image as possible in the format required by the journal.
We are somewhat concerned about figure/table size within the print form
of the journal.

[Response:]

After trying a substantial number of different approaches, I believe the best way to 
solve this problem is to fundamentally change the set-up of the birth spacing analysis.
First examining how average birth spacing changed and then have a separate subsection on 
distribution resulted in many graphs that each would become very small and hard to read.
Instead, I now present three percentile birth intervals---25th, median, and 75th---together
with the sex ratio and the parity progression probability.
Furthermore, to keep within the figure/table limit and not have multiple-page figures,
I moved the results for urban women without education and rural women with twelve or more 
years of education to the online Appendix.

The main advantage of this new approach, beside making the figures less challenging to 
read, is that it more clearly ties the section directly to the main question I am asking.
Furthermore, the new set-up makes it easier to understand similarities and differences 
across groups and compare the results to the prior literature, as well as ties the
birth spacing discussion directly to the fertility section that follows.

The rewritten section proceeds in three parts.
I now first present the broad trends for parity progression and sex ratio to set the
stage for the analysis.

Next, I discuss how birth spacing has changed in situations where there is the least use
of sex selection (less educated women and among better educated women with one or more
sons).
To this part, I have added a discussion of how these results compare with what the
prior literature has found \citep{Rutstein2011,Casterline2016}.
To tie the results to the labor force participation, I also show how average spacing
have increased the most for the women least likely to work.
Finally, I show how the longest spacing has changed with declining fertility, and suggest 
reasons why the best-educated women appear to be different from what has been observed 
among other groups in India and elsewhere.

The last part examines how birth spacing changed with use of sex selection.
I use the third spell for the best-educated women as an illustration, especially the
very rapid increase right after the introduction of sex selection.
I then show where the reversal of the traditional spacing pattern occurred.
As part of my response to reviewer 2's question about the period grouping, I have 
included a discussion of whether the predicted decline in the use of sex selection
came about.
I end with a summary of results to tie the section to the fertility section.

@@

[Response:]

I have rewritten the Introduction to emphasize the main question I address
(``how did birth spacing respond to these changes, especially the introduction and spread 
of sex selection?'') and the two questions addressing the effects of changes in 
birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
estimates?'' and `` how do the changes in birth spacing and the increased use of abortions 
impact children's chances of survival?'').

Following the three questions, I now outline how the study progresses focusing on 
how I examine each of the three questions, including the key outcomes and key explanatory 
variables.
To prevent exceeding the word count I have also edited the entire introduction.
Although sligthly longer than original, it is still less than 900 words 
(not counting references).

I have edited the introduction of each section to highlight what I question
I am addressing.
Furthermore, I have removed some of the repetition in, for example, the
discussion of tempo effects and mortality, so that the motivation is now only
in the Introduction rather than being spread over the Introduction and the
other sections.

Finally, I have completely redone the discussion of how spacing changed as described
above.
I hope this will make it easier for the reader to see the answer to the main
question of the paper.

### 2020-08-11 paper/sex_selection_spacing-ver4.tex
Add better figure captions

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_rural}
\caption{combined graphs - low rural}
\label{fig:spacing_low_rural}
\end{figure}

% \begin{figure}
% \centering
% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
% \caption{combined graphs - low urban}
% \label{fig:spacing_low_urban}
% \end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_rural}
\caption{combined graphs - med rural}
\label{fig:spacing_med_rural}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
\caption{combined graphs - med urban}
\label{fig:spacing_med_urban}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_rural}
\caption{combined graphs - high rural}
\label{fig:spacing_high_rural}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
\caption{combined graphs - high urban}
\label{fig:spacing_high_urban}
\end{figure}

% \begin{figure}
% \centering
% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
% \caption{combined graphs - highest rural}
% \label{fig:spacing_highest_rural}
% \end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_urban}
\caption{combined graphs - highest urban}
\label{fig:spacing_highest_urban}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_low_med}
\caption{Mortality low medium}
\label{fig:mortality_low_med}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_high_highest}
\caption{Mortality high highest}
\label{fig:mortality_high_highest}
\end{figure}

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
\caption{combined graphs - low urban}
\label{fig:spacing_low_urban}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
\caption{combined graphs - highest rural}
\label{fig:spacing_highest_rural}
\end{figure}

@@

>>>>

\captionsetup[figure]{skip = -16}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_rural}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for rural women with no education by spell, sex composition, and period}
\label{fig:spacing_low_rural}
\end{figure}

% \begin{figure}
% \centering
% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
% \caption{Percentile birth intervals, sex ratios, and parity progression  
% for urban women with no education by spell, sex composition, and period}
% \label{fig:spacing_low_urban}
% \end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_rural}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for rural women with one to seven years of education by spell, sex composition, and period}
\label{fig:spacing_med_rural}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for urban women with one to seven years of education by spell, sex composition, and period}
\label{fig:spacing_med_urban}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_rural}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for rural women with eight to eleven years of education by spell, sex composition, and period}
\label{fig:spacing_high_rural}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for urban women with eight to eleven years of education by spell, sex composition, and period}
\label{fig:spacing_high_urban}
\end{figure}

% \begin{figure}
% \centering
% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
% \caption{Percentile birth intervals, sex ratios, and parity progression  
% for rural women with twelve or more years of education by spell, sex composition, and period}
% \label{fig:spacing_highest_rural}
% \end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_urban}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for urban women with twelve or more years of education by spell, sex composition, and period}
\label{fig:spacing_highest_urban}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_low_med}
\caption{Infant mortality by preceding birth interval across periods for women with 
no education and women with one to seven years of education}
\label{fig:mortality_low_med}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_high_highest}
\caption{Infant mortality by preceding birth interval across periods for women with 
eight to eleven and twelve and above years of education}
\label{fig:mortality_high_highest}
\end{figure}

@@

\captionsetup[figure]{skip = 10}

@@

\captionsetup[figure]{skip = -16}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for urban women with no education by spell, sex composition, and period}
\label{fig:spacing_low_urban}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
\caption{Percentile birth intervals, sex ratios, and parity progression  
for rural women with twelve or more years of education by spell, sex composition, and period}
\label{fig:spacing_highest_rural}
\end{figure}

@@

\captionsetup[figure]{skip = 5}
